---
title: "DE Unsupervised - gender corrected"
author: "Mafe Senosain"
date: "5/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('/Users/senosam/Documents/Repositories/Research/data_analysis_rnaseq/R/30_DEGanalysis.R')
environment_set()
```

# Pre-processing of the data
```{r}
ls_preprocessed <- preprocess_rna(path_rnaseq = 'rnaseq.RData', correct_batch = T, correct_gender = T)
x <- data.frame(ls_preprocessed$vsd_mat)
x <- cbind('ID'=rownames(x), x)
#x <- cbind('ID'=ls_preprocessed$rna_all$Feature_gene_name, x)
#write.table(x, file = "vst_normed.txt", sep = "\t", row.names = F, quote = F)

```

# Exploring data

## Batch effect correction
```{r}
print(ls_preprocessed$pbatch_bf)
print(ls_preprocessed$pgender_bf)
print(ls_preprocessed$pbatch_af)
print(ls_preprocessed$pgender_af)
```


## Using all genes

```{r}
names(ls_preprocessed)
dim(ls_preprocessed$vsd_mat)
corr_pt <- Hmisc::rcorr(ls_preprocessed$vsd_mat, type = 'spearman')
Heatmap(corr_pt$r, name = "mat", 
        #column_km = 3, 
        #row_km = 3,
        heatmap_legend_param = list(color_bar = "continuous"), 
        row_names_gp = gpar(fontsize = 8),
        column_names_gp = gpar(fontsize = 8))

# Hierarchical clustering
d <- dist(corr_pt$r)
hc1 <- hclust(d)
plot(hc1, cex = 0.6, hang = -1)

#clustering
k <- 4
hc1 <- hclust(d, method = 'complete')
hc2 <- hclust(d, method = 'average')
hc3 <- hclust(d, method = 'mcquitty')
hc4 <- hclust(d, method = 'ward.D')

sub_grp1 <- cutree(hc1, k = k)
sub_grp2 <- cutree(hc2, k = k)
sub_grp3 <- cutree(hc3, k = k)
sub_grp4 <- cutree(hc4, k = k)
kmns <- kmeans(corr_pt$r, centers = k)
clusters <- as.data.frame(cbind(Vantage_ID=names(sub_grp1), 
                                hclust_com=sub_grp1, 
                                hclust_ave=sub_grp2, 
                                hclust_mq=sub_grp3, 
                                hclust_w=sub_grp4, 
                                k_means = kmns$cluster))

ha = rowAnnotation(

    hclust_com = as.factor(clusters$hclust_com),
    hclust_ave = as.factor(clusters$hclust_ave),
    hclust_mq = as.factor(clusters$hclust_mq),
    hclust_w = as.factor(clusters$hclust_w),
    k_means = as.factor(clusters$k_means),

    simple_anno_size = unit(0.5, "cm")
)

Heatmap(corr_pt$r, name = "mat", 
        heatmap_legend_param = list(color_bar = "continuous"), 
        row_names_gp = gpar(fontsize = 8),
        column_names_gp = gpar(fontsize = 8), right_annotation = ha)

```

## Clustering

```{r}
p_all_cl <- ls_preprocessed$p_all
p_all_cl <- p_all_cl %>% 
              inner_join(., clusters, "Vantage_ID") %>%
              mutate_all(as.character)

```

# DE analysis

```{r}
DE_res <- DE_analysis(ls_preprocessed, 
           GeneBased=FALSE, 
           pDataBased=FALSE,
           NewCondition=TRUE,
           NewCondition_df = p_all_cl,
           cond_nm='hclust_com',
           two_levels=c('1','2'),
           reference = '1',
           correct_gender=TRUE)

```

## DE results
```{r}
heatmap_200(DE_res$res_df, DE_res$vsd_mat_sym, DE_res$meta_data, DE_res$pData_rnaseq)
volcano_plot(DE_res$res_df, gene=NULL, p_title='Clusters: 1 vs 2')

```

## Pathway enrichment analysis fGSEA
CANARY Good prognosis (G) is the reference. When sample is P, pathways shown below are up- or down- regulated
```{r}
fgsea_res <- fgsea_analysis(DE_res)

fgsea_plot(fgsea_res$res_hm, pathways_title='Hallmark', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_c1, pathways_title='C1 positional genes', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_c2, pathways_title='C2 curated genes', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_c3, pathways_title='C3 regulatory target genes', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_c4, pathways_title='C4 cancer', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_c5, pathways_title='C5 GO genes', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_c6, pathways_title='C6 oncogenic', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_c7, pathways_title='C7 immunologic', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_msg, pathways_title='All signatures', condition_name='CANARY: G vs P')
```



## Selecting top genes with Clust

```{r}
gene_ID <-read.delim("~/Documents/Massion_lab/RNASeq_summary/Results_02_Jun_20_1/Clusters_Objects.tsv")[-1,]
top_genes <-  sort(as.character(unique(as.vector(as.matrix(gene_ID)))))[-1]

corr_pt <- Hmisc::rcorr(ls_preprocessed$vsd_mat[top_genes,], type = 'spearman')
Heatmap(corr_pt$r, name = "mat", 
        #column_km = 3, 
        #row_km = 3,
        heatmap_legend_param = list(color_bar = "continuous"), 
        row_names_gp = gpar(fontsize = 8),
        column_names_gp = gpar(fontsize = 8))

# Hierarchical clustering
d <- dist(corr_pt$r)
hc1 <- hclust(d)
plot(hc1, cex = 0.6, hang = -1)

#clustering
k <- 3
hc1 <- hclust(d, method = 'complete')
hc2 <- hclust(d, method = 'average')
hc3 <- hclust(d, method = 'mcquitty')
hc4 <- hclust(d, method = 'ward.D')

sub_grp1 <- cutree(hc1, k = k)
sub_grp2 <- cutree(hc2, k = k)
sub_grp3 <- cutree(hc3, k = k)
sub_grp4 <- cutree(hc4, k = k)
kmns <- kmeans(corr_pt$r, centers = k)
clusters <- as.data.frame(cbind(Vantage_ID=names(sub_grp1), 
                                hclust_com=sub_grp1, 
                                hclust_ave=sub_grp2, 
                                hclust_mq=sub_grp3, 
                                hclust_w=sub_grp4, 
                                k_means = kmns$cluster))

ha = rowAnnotation(

    hclust_com = as.factor(clusters$hclust_com),
    hclust_ave = as.factor(clusters$hclust_ave),
    hclust_mq = as.factor(clusters$hclust_mq),
    hclust_w = as.factor(clusters$hclust_w),
    k_means = as.factor(clusters$k_means),

    simple_anno_size = unit(0.5, "cm")
)

Heatmap(corr_pt$r, name = "mat", 
        heatmap_legend_param = list(color_bar = "continuous"), 
        row_names_gp = gpar(fontsize = 8),
        column_names_gp = gpar(fontsize = 8), right_annotation = ha)


```



## Clustering

```{r}
p_all_cl <- ls_preprocessed$p_all
p_all_cl <- p_all_cl %>% 
              inner_join(., clusters, "Vantage_ID") %>%
              mutate_all(as.character)

ls_preprocessed$rna_all <- ls_preprocessed$rna_all[which(ls_preprocessed$rna_all$Feature %in% top_genes),]
ls_preprocessed$counts_all <- ls_preprocessed$counts_all[top_genes,]
ls_preprocessed$vsd_mat <- ls_preprocessed$vsd_mat[top_genes,]

```

# DE analysis

```{r}
DE_res <- DE_analysis(ls_preprocessed, 
           GeneBased=FALSE, 
           pDataBased=FALSE,
           NewCondition=TRUE,
           NewCondition_df = p_all_cl,
           cond_nm='k_means',
           two_levels=c('2','3'),
           reference = '2',
           correct_gender=TRUE)

```

## DE results
```{r}
heatmap_200(DE_res$res_df, DE_res$vsd_mat_sym, DE_res$meta_data, DE_res$pData_rnaseq)
volcano_plot(DE_res$res_df, gene=NULL, p_title='Clusters: 2 vs 3')

```

## Pathway enrichment analysis fGSEA
CANARY Good prognosis (G) is the reference. When sample is P, pathways shown below are up- or down- regulated
```{r}
fgsea_res <- fgsea_analysis(DE_res)

fgsea_plot(fgsea_res$res_hm, pathways_title='Hallmark', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_c1, pathways_title='C1 positional genes', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_c2, pathways_title='C2 curated genes', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_c3, pathways_title='C3 regulatory target genes', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_c4, pathways_title='C4 cancer', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_c5, pathways_title='C5 GO genes', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_c6, pathways_title='C6 oncogenic', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_c7, pathways_title='C7 immunologic', condition_name='CANARY: G vs P')
fgsea_plot(fgsea_res$res_msg, pathways_title='All signatures', condition_name='CANARY: G vs P')
```


```{r}
names(ls_preprocessed)

n_genes <- 500
vsd_mat <- ls_preprocessed$vsd_mat
variances <- apply(vsd_mat, 1, var)
top_genes <- data.frame(vsd_mat) %>%
  mutate(gene=rownames(.),
         symbol=ls_preprocessed$rna_all$Feature_gene_name,
         variances = variances) %>%
  arrange(desc(variances)) %>%
  dplyr::select(gene, symbol) %>%
  head(n_genes)
vsd_mat5k<- vsd_mat[top_genes$gene,]
rownames(vsd_mat5k) <- top_genes$symbol

idx <- grep('HLA-DRB1', ls_preprocessed$rna_all$Feature_gene_name)
hla_sym <- as.character(ls_preprocessed$rna_all$Feature_gene_name[idx])

vsd_mat5k <- vsd_mat5k[which(rownames(vsd_mat5k)%in% hla_sym),]
dim(vsd_mat5k)


corr_pt <- Hmisc::rcorr(vsd_mat5k, type = 'spearman')
# Hierarchical clustering
d <- dist(corr_pt$r)
hc1 <- hclust(d)
plot(hc1, cex = 0.6, hang = -1)

corr_gn <- Hmisc::rcorr(t(vsd_mat5k), type = 'spearman')
# Hierarchical clustering
d <- dist(corr_gn$r)
hc1 <- hclust(d)
plot(hc1, cex = 0.6, hang = -1)

Heatmap(corr_pt$r, name = "mat", 
        column_km = 2, 
        row_km = 2,
        heatmap_legend_param = list(color_bar = "continuous"), 
        row_names_gp = gpar(fontsize = 8),
        column_names_gp = gpar(fontsize = 8))

Heatmap(corr_gn$r, name = "mat", 
        column_km = 2, 
        row_km = 2,
        heatmap_legend_param = list(color_bar = "continuous"), 
        row_names_gp = gpar(fontsize = 8),
        column_names_gp = gpar(fontsize = 8))

Heatmap(vsd_mat5k, name = "mat", 
        column_km = 2, 
        row_km = 2,
        heatmap_legend_param = list(color_bar = "continuous"), 
        row_names_gp = gpar(fontsize = 8),
        column_names_gp = gpar(fontsize = 8))

```


```{r}
names(ls_preprocessed)

n_genes <- 5000
vsd_mat <- ls_preprocessed$vsd_mat
variances <- apply(vsd_mat, 1, var)
top_genes <- data.frame(vsd_mat) %>%
  mutate(gene=rownames(.),
         symbol=ls_preprocessed$rna_all$Feature_gene_name,
         variances = variances) %>%
  arrange(desc(variances)) %>%
  dplyr::select(gene, symbol) %>%
  head(n_genes)
vsd_mat5k<- vsd_mat[top_genes$gene,]
rownames(vsd_mat5k) <- top_genes$symbol

idx <- grep('HLA-DR', ls_preprocessed$rna_all$Feature_gene_name)
hla_id <- as.character(ls_preprocessed$rna_all$Feature[idx])
hla_sym <- as.character(ls_preprocessed$rna_all$Feature_gene_name[idx])

k <- which(hla_id %in% top_genes$gene)
as_tibble(cbind(hla_id[k],hla_sym[k]))

vsd_mat5k <- vsd_mat5k[which(rownames(vsd_mat5k)%in% hla_sym),]
dim(vsd_mat5k)




corr_pt <- Hmisc::rcorr(vsd_mat5k, type = 'spearman')
# Hierarchical clustering
d <- dist(corr_pt$r)
hc1 <- hclust(d)
plot(hc1, cex = 0.6, hang = -1)
sub_grp <- cutree(hc1, k = 2)
clusters <- as.data.frame(cbind(Vantage_ID=names(sub_grp), Cluster=sub_grp))

corr_gn <- Hmisc::rcorr(t(vsd_mat5k), type = 'spearman')
# Hierarchical clustering
d <- dist(corr_gn$r)
hc1 <- hclust(d)
plot(hc1, cex = 0.6, hang = -1)

set.seed(455)
Heatmap(corr_pt$r, name = "mat", 
        column_km = 2, 
        row_km = 2,
        heatmap_legend_param = list(color_bar = "continuous"), 
        row_names_gp = gpar(fontsize = 8),
        column_names_gp = gpar(fontsize = 8))

Heatmap(corr_gn$r, name = "mat", 
        column_km = 2, 
        row_km = 2,
        heatmap_legend_param = list(color_bar = "continuous"), 
        row_names_gp = gpar(fontsize = 8),
        column_names_gp = gpar(fontsize = 8))

Heatmap(vsd_mat5k, name = "mat", 
        column_km = 2, 
        row_km = 2,
        heatmap_legend_param = list(color_bar = "continuous"), 
        row_names_gp = gpar(fontsize = 8),
        column_names_gp = gpar(fontsize = 8))



```


```{r}
names(ls_preprocessed)

n_genes <- 5000
vsd_mat <- ls_preprocessed$vsd_mat
variances <- apply(vsd_mat, 1, var)
top_genes <- data.frame(vsd_mat) %>%
  mutate(gene=rownames(.),
         symbol=ls_preprocessed$rna_all$Feature_gene_name,
         variances = variances) %>%
  arrange(desc(variances)) %>%
  dplyr::select(gene, symbol) %>%
  head(n_genes)
vsd_mat5k<- vsd_mat[top_genes$gene,]
rownames(vsd_mat5k) <- top_genes$gene

idx <- grep('HLA-DR', ls_preprocessed$rna_all$Feature_gene_name)
hla_id <- as.character(ls_preprocessed$rna_all$Feature[idx])
hla_sym <- as.character(ls_preprocessed$rna_all$Feature_gene_name[idx])

k <- which(hla_id %in% top_genes$gene)
as_tibble(cbind(hla_id[k],hla_sym[k]))

vsd_mat5k <- vsd_mat5k[which(rownames(vsd_mat5k)%in% hla_id),]
dim(vsd_mat5k)




corr_pt <- Hmisc::rcorr(vsd_mat5k, type = 'spearman')
# Hierarchical clustering
d <- dist(corr_pt$r)
hc1 <- hclust(d)
plot(hc1, cex = 0.6, hang = -1)

corr_gn <- Hmisc::rcorr(t(vsd_mat5k), type = 'spearman')
# Hierarchical clustering
d <- dist(corr_gn$r)
hc1 <- hclust(d)
plot(hc1, cex = 0.6, hang = -1)

set.seed(455)
Heatmap(corr_pt$r, name = "mat", 
        column_km = 2, 
        row_km = 2,
        heatmap_legend_param = list(color_bar = "continuous"), 
        row_names_gp = gpar(fontsize = 8),
        column_names_gp = gpar(fontsize = 8))

Heatmap(corr_gn$r, name = "mat", 
        column_km = 2, 
        row_km = 2,
        heatmap_legend_param = list(color_bar = "continuous"), 
        row_names_gp = gpar(fontsize = 8),
        column_names_gp = gpar(fontsize = 8))

Heatmap(vsd_mat5k, name = "mat", 
        column_km = 2, 
        row_km = 2,
        heatmap_legend_param = list(color_bar = "continuous"), 
        row_names_gp = gpar(fontsize = 8),
        column_names_gp = gpar(fontsize = 8))

```

