---
title: "TMA36 RNA Seq dataset: Indolent vs. Intermediate vs. Aggressive"
author: "Mafe Senosain"
date: "`r Sys.Date()`"
output:
    html_document:
        toc: true
        toc_float: true
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
source('/Users/senosam/Documents/Repositories/Research/data_analysis_rnaseq/R/30_DEGanalysis.R')
source("/Users/senosam/Documents/Repositories/Research/data_analysis_cytof/R/51_supervised_analysis_viz.R")
source("/Users/senosam/Documents/Repositories/Research/data_analysis_cytof/R/20_ClustAnnot_functions.R")
load("/Users/senosam/Documents/Massion_lab/RNASeq_summary/rnaseq.RData")
environment_set()
```


```{r}
# Preprocessing data
ls_preprocessed <- preprocess_rna(path_rnaseq = '/Users/senosam/Documents/Massion_lab/RNASeq_summary/rnaseq.RData', 
                                  correct_batch = F, lowvargenesrm = T, prot_coding_only = F, xychr_rm = T)

CDE <- read.csv(file = '/Users/senosam/Documents/Massion_lab/CyTOF_summary/CDE_TMA36_2021JAN13_SA_MF.csv')
pData_rnaseq <- CDE[match(ls_preprocessed$pData_rnaseq$pt_ID, CDE$pt_ID),]
ls_preprocessed$pData_rnaseq <- pData_rnaseq

# adding FPKM
rownames(fpkm_all) <- fpkm_all$Feature
fpkm_all <- fpkm_all[match(ls_preprocessed$rna_all$Feature, rownames(fpkm_all)),]
fpkm_all <- fpkm_all[,ls_preprocessed$p_all$Vantage_ID]
ls_preprocessed$fpkm_all <- as.matrix(fpkm_all)

# adding TPM
rownames(tpm_all) <- rna_all$Feature
tpm_all <- tpm_all[match(ls_preprocessed$rna_all$Feature, rownames(tpm_all)),]
tpm_all <- tpm_all[,ls_preprocessed$p_all$Vantage_ID]
ls_preprocessed$tpm_all <- tpm_all
```

# Indolent vs Aggressive
## Differential gene expression analysis

```{r echo=FALSE}
DE_res <- DE_analysis(ls_preprocessed, 
           GeneBased=FALSE, 
           pDataBased=TRUE,
           NewCondition=FALSE,
           cond_nm='n_op2',
           two_levels=c('agg','ind'),
           reference = 'ind')

```

### Top DE genes: Heatmap

```{r echo=FALSE, fig.width = 7, fig.height = 12}
heatmap_200(DE_res$res_df, DE_res$vsd_mat_sym, DE_res$meta_data, DE_res$pData_rnaseq, scale_mat = T)
```

### Top DE genes: Volcano plot

```{r echo=FALSE}
volcano_plot(DE_res$res_df, gene=NULL, p_title='Indolent vs Aggressive')
```

### Top DE genes: table (cutoffs: pval\<0.05, L2FC \> 1.5)

<div>

> -   baseMean---The average of the normalized count values, dividing by size factors, taken over all samples.
>
> -   log2FoldChange--The effect size estimate.
>     This value indicates how much the gene or transcript's expression seems to have changed between the comparison and control groups.
>     This value is reported on a logarithmic scale to base 2.
>
> -   lfcSE--The standard error estimate for the log2 fold change estimate.
>
> -   stat--The value of the test statistic for the gene or transcript.
>
> -   pvalue--P-value of the test for the gene or transcript.
>
> -   padj--Adjusted P-value for multiple testing for the gene or transcript.
>
> -   gene-Gene ID from ENSEMBL database
>
> -   Symbol---Gene name

</div>

```{r}
l2fc_cutoff=1.5
pval_cutoff = 0.05
res_df <- data.frame(DE_res$res_df) %>%
  na.omit() %>%
  filter(abs(log2FoldChange) > l2fc_cutoff) %>%
  filter(pvalue < pval_cutoff) %>%
  arrange(pvalue)
rownames(res_df) <- NULL
knitr::kable(res_df)
```

## Pathway enrichment analysis fGSEA

Indolent (n_op2 = 'ind') is the reference.
When sample is Aggressive ('agg'), pathways shown below are up- or down- regulated

> -   pathway -- name of the pathway as in 'names(pathway)';
>
> -   pval -- an enrichment p-value;
>
> -   padj -- a BH-adjusted p-value;
>
> -   log2err -- the expected error for the standard deviation of the P-value logarithm.
>
> -   ES -- enrichment score, same as in Broad GSEA implementation;
>
> -   NES -- enrichment score normalized to mean enrichment of random samples of the same size; • size -- size of the pathway after removing genes not present in 'names(stats)'.
>
> -   leadingEdge -- vector with indexes of leading edge genes that drive the enrichment, see [http://software.broadinstitute.org/gsea/doc/GSEAUserGuideTEXT.htm\\\#\\\_Running_a\\\_Leading](http://software.broadinstitute.org/gsea/doc/GSEAUserGuideTEXT.htm#_Running_a_Leading){.uri}.

```{r echo=FALSE}
fgsea_res <- fgsea_analysis(DE_res)
```

### Hallmark Pathways

```{r echo=FALSE, fig.width = 15, fig.height = 10}
fgsea_plot(fgsea_res$res_hm, pathways_title='Hallmark', condition_name='Indolent vs Aggressive')
```

### C1 positional genes Pathways

```{r echo=FALSE, fig.width = 15, fig.height = 10}
fgsea_plot(fgsea_res$res_c1, pathways_title='C1 positional genes', condition_name='Indolent vs Aggressive')
```

### C2 curated genes Pathways

```{r echo=FALSE, fig.width = 15, fig.height = 10}
fgsea_plot(fgsea_res$res_c2, pathways_title='C2 curated genes', condition_name='Indolent vs Aggressive')
```

### C3 regulatory target genes Pathways

```{r echo=FALSE, fig.width = 15, fig.height = 10}
fgsea_plot(fgsea_res$res_c3, pathways_title='C3 regulatory target genes', condition_name='Indolent vs Aggressive')
```

### C4 cancer Pathways

```{r echo=FALSE, fig.width = 15, fig.height = 10}
fgsea_plot(fgsea_res$res_c4, pathways_title='C4 cancer', condition_name='Indolent vs Aggressive')
```

### C5 GO genes Pathways

```{r echo=FALSE, fig.width = 15, fig.height = 10}
fgsea_plot(fgsea_res$res_c5, pathways_title='C5 GO genes', condition_name='Indolent vs Aggressive')
```

### C6 oncogenic Pathways

```{r echo=FALSE, fig.width = 15, fig.height = 10}
fgsea_plot(fgsea_res$res_c6, pathways_title='C6 oncogenic', condition_name='Indolent vs Aggressive')
```

### C7 immunologic Pathways

```{r echo=FALSE, fig.width = 15, fig.height = 10}
fgsea_plot(fgsea_res$res_c7, pathways_title='C7 immunologic', condition_name='Indolent vs Aggressive')
```

### All signatures Pathways

```{r echo=FALSE, fig.width = 15, fig.height = 10}
fgsea_plot(fgsea_res$res_msg, pathways_title='All signatures', condition_name='Indolent vs Aggressive')
```

### REACTOME Pathways

```{r echo=FALSE, fig.width = 15, fig.height = 10}
fgsea_plot(fgsea_res$res_rtm, pathways_title='REACTOME', condition_name='Indolent vs Aggressive')
```

## KEGG pathway analysis

```{r echo=FALSE, fig.width = 15, fig.height = 10}
keggres <- kegg_go(DE_res, kegg = T, GO = F)
keggGO_plot(keggres, pathways_title='KEGG', cutoff = 0.05, 
             max_pathways = 10, condition_name='Indolent vs Aggressive', pval_colnm='p.val')
```

## Gene Ontology analysis

```{r echo=FALSE, fig.width = 15, fig.height = 10}
keggres <- kegg_go(DE_res, kegg = F, GO = T)
keggGO_plot(keggres, pathways_title='GO', cutoff = 0.05, 
             max_pathways = 10, condition_name='Indolent vs Aggressive', pval_colnm='p.val')
```

# Associations of MHC-II related genes with SILA

```{r}
hla_i <- grep('^HLA', ls_preprocessed$rna_all$Feature_gene_name)
hla_ids <- as.character(ls_preprocessed$rna_all$Feature[hla_i])
hla_gsym <- as.character(ls_preprocessed$rna_all$Feature_gene_name[hla_i])
```

```{r}
# Filter MHC-II related genes from DE genes
de_hla <- data.frame(DE_res$res)[hla_ids,] %>%
  mutate(gene=hla_gsym) %>%
  arrange(desc(abs(log2FoldChange))) %>%
  slice(which(pvalue<0.05))
```

## Compare MHC-II related genes I vs A

```{r}
hm_genes <- function(ls_preprocessed, mat_name, hla_ids, hla_gsym, scale_mat = TRUE){
  int_idx <- which(ls_preprocessed$pData_rnaseq$n_op2 == 'int')
  mat <- as.matrix(ls_preprocessed[[mat_name]])
  mat <- mat[,-int_idx]
  mat <- mat[hla_ids,]
  ha = HeatmapAnnotation(
    Condition = as.factor(ls_preprocessed$pData_rnaseq$n_op2[-int_idx]),
    SILA = ls_preprocessed$pData_rnaseq$SILA[-int_idx],
    Stage = ls_preprocessed$pData_rnaseq$Stages_simplified[-int_idx],
    simple_anno_size = unit(0.5, "cm")
  )
  if(scale_mat){
    mat <- t(scale(t(mat)))
  }
  rownames(mat) <- hla_gsym
  Heatmap(mat, name = "mat", 
    column_split = as.factor(ls_preprocessed$pData_rnaseq$n_op2[-int_idx]),
    heatmap_legend_param = list(color_bar = "continuous"), 
    row_names_gp = gpar(fontsize = 8),
    column_names_gp = gpar(fontsize = 8), top_annotation = ha)
  
}
```

### Using VST normed genes

```{r}
hm_genes(ls_preprocessed, 'vsd_mat', hla_ids, hla_gsym, scale_mat = T)
hm_genes(ls_preprocessed, 'vsd_mat', rownames(de_hla), de_hla$gene, scale_mat = T)
```

### Using TPM normed genes

```{r}
hm_genes(ls_preprocessed, 'tpm_all', hla_ids, hla_gsym, scale_mat = T)
hm_genes(ls_preprocessed, 'tpm_all', rownames(de_hla), de_hla$gene, scale_mat = T)
```

### Using FPKM normed genes

```{r}
hm_genes(ls_preprocessed, 'fpkm_all', hla_ids, hla_gsym, scale_mat = T)
hm_genes(ls_preprocessed, 'fpkm_all', rownames(de_hla), de_hla$gene, scale_mat = T)
```

## PCA of patients using MHC-II related genes

```{r}
pca_hla <- function(ls_preprocessed, mat_name, hla_ids, scale_mat = TRUE){
  int_idx <- which(ls_preprocessed$pData_rnaseq$n_op2 == 'int')
  mat <- data.frame(t(ls_preprocessed[[mat_name]][hla_ids,]))
  mat <- cbind(mat, 'SILA'=ls_preprocessed$pData_rnaseq$SILA,
                              "n_op2"=ls_preprocessed$pData_rnaseq$n_op2)
  mat <- mat[-int_idx,]
  
  x <- mat[,-which(colnames(mat) %in% c("SILA","n_op2"))]
  
  if(scale_mat){
    x <- scale(x)
  }
  pca_hla <- cbind(data.frame(prcomp(x)$x), 'SILA'=mat$SILA,
                              "n_op2"=mat$n_op2)
  ggplot(pca_hla, aes(PC1, PC2, color = n_op2)) +
    geom_point()
  
}
```

### Using VST normed genes

```{r}
pca_hla(ls_preprocessed, mat_name='vsd_mat', hla_ids, scale_mat = F)
pca_hla(ls_preprocessed, mat_name='vsd_mat', hla_ids, scale_mat = T)
```

### Using TPM normed genes

```{r}
pca_hla(ls_preprocessed, mat_name='tpm_all', hla_ids, scale_mat = F)
pca_hla(ls_preprocessed, mat_name='tpm_all', hla_ids, scale_mat = T)
```

### Using FPKM normed genes

```{r}
pca_hla(ls_preprocessed, mat_name='fpkm_all', hla_ids, scale_mat = F)
pca_hla(ls_preprocessed, mat_name='fpkm_all', hla_ids, scale_mat = T)
```

## Compare MHC-II related genes I vs A

```{r}
compare_hla <- function(ls_preprocessed, mat_name, hla_ids, hla_gsym, BPplot = T){
  int_idx <- which(ls_preprocessed$pData_rnaseq$n_op2 == 'int')
  mat <- data.frame(t(ls_preprocessed[[mat_name]][hla_ids,]))
  mat <- cbind(mat, 'SILA'=ls_preprocessed$pData_rnaseq$SILA,
                              "n_op2"=ls_preprocessed$pData_rnaseq$n_op2)
  mat <- mat[-int_idx,]
  
  sum_df <- data.frame(matrix(nrow = 0, ncol = 4))
  ind <- which(mat$n_op2 == 'ind')
  for (i in colnames(mat)[grep("ENS",colnames(mat))]){
    ind_med <- median(mat[ind,i])
    agg_med <- median(mat[-ind,i])
    pval <- wilcox.test(mat[ind,i], mat[-ind,i])
    sum_df <- rbind(sum_df, c(i,ind_med, agg_med, pval$p.value))
  }
  colnames(sum_df) <- c('Gene', 'Median.Ind', 'Median.Agg', 'p.value')
  sum_df['p.adjusted'] <- p.adjust(sum_df$p.value, method = "BH")
  sum_df <- cbind('Symbol'=hla_gsym, sum_df)
  sum_df <- sum_df %>%
    arrange(p.value) %>%
    slice(which(p.value < 0.09))
  
  #print(sum_df)
  
  # boxplots
  if(BPplot){
    x <- mat[,sum_df$Gene]
    colnames(x) <- sum_df$Symbol
    x['n_op2'] <- mat$n_op2
    x <- reshape2::melt(x)
    lb <- x$n_op2
    lb[which(x[,'n_op2'] == 'agg')] <- 'Aggressive'
    lb[-which(x[,'n_op2'] == 'agg')] <- 'Indolent'
    levels = c('Indolent', 'Aggressive')
    x['n_op2'] <- factor(lb, levels = levels)
    
    comp =  list(c("Indolent", "Aggressive"))
    colr = c("#3498DB", "#EC7063")
    
    if(nrow(sum_df)>1){
      ggplot(x, aes(x=n_op2, y=value, color = n_op2)) +
        geom_boxplot() +
        ggsignif::geom_signif(comparisons = comp, 
                              map_signif_level=TRUE) +
        facet_wrap(~variable, scales='free') +
        theme(plot.title = element_text(hjust = 0.5, size=22))+
        scale_color_manual(values=colr, name = "Behavior")       
    }else{
      #ggplot(x, aes(x=n_op2, y=value, color = n_op2)) +
    }
   
  }
  knitr::kable(sum_df)

}
```

### Using VST normed genes

```{r echo=FALSE, fig.width = 8, fig.height = 3}
compare_hla(ls_preprocessed, mat_name='vsd_mat', hla_ids, hla_gsym,  BPplot = T)
compare_hla(ls_preprocessed, mat_name='vsd_mat', rownames(de_hla), de_hla$gene, BPplot = FALSE)
```

### Using TPM normed genes

```{r echo=FALSE, fig.width = 8, fig.height = 3}
compare_hla(ls_preprocessed, mat_name='tpm_all', hla_ids, hla_gsym, BPplot = T)
compare_hla(ls_preprocessed, mat_name='tpm_all', rownames(de_hla), de_hla$gene, BPplot = FALSE)
```

### Using FPKM normed genes

```{r echo=FALSE, fig.width = 8, fig.height = 3}
compare_hla(ls_preprocessed, mat_name='fpkm_all', hla_ids, hla_gsym, BPplot = T)
compare_hla(ls_preprocessed, mat_name='fpkm_all', rownames(de_hla), de_hla$gene,  BPplot = FALSE)
```

# Transcription Factor activity (VIPER)

For documentation click here <https://bioconductor.org/packages/release/bioc/vignettes/viper/inst/doc/viper.pdf>

```{r}
library(viper)
dorothea2viper_regulons <- function(df) {
  regulon_list <- split(df, df$tf)
  viper_regulons <- lapply(regulon_list, function(regulon) {
    tfmode <- stats::setNames(regulon$mor, regulon$target)
    list(tfmode = tfmode, likelihood = rep(1, length(tfmode)))
  })
  return(viper_regulons)
}


result <- WGCNA::collapseRows(ls_preprocessed$vsd_mat,
                          rowGroup=ls_preprocessed$rna_all$Feature_gene_name,
                          rowID=rownames(ls_preprocessed$vsd_mat),
                          method="MaxMean")

data <- data.frame(result$datETcollapsed)

regulons = dorothea::dorothea_hs %>%
  filter(confidence %in% c("A", "B"))

regu <- dorothea2viper_regulons(regulons)
vpres_25 <- t(viper(data, regu, verbose = FALSE, minsize = 25))
rownames(vpres_25) <- ls_preprocessed$p_all$pt_ID

vpres_4 <- t(viper(data, regu, verbose = FALSE, minsize = 4))
rownames(vpres_4) <- ls_preprocessed$p_all$pt_ID

# Differential activity inference
ind_ii = which(ls_preprocessed$pData_rnaseq$n_op2=='ind')
agg_ii = which(ls_preprocessed$pData_rnaseq$n_op2=='agg')
t_vpres_4 <- t(vpres_4)
tmp = rowTtest(t_vpres_4[,agg_ii], t_vpres_4[,ind_ii])
data.frame(Gene = rownames(tmp$p.value), t = round(tmp$statistic, 2),"p-value" = signif(tmp$p.value, 3))[order(tmp$p.value)[1:10], ]
```

## Comparing two groups with msVIPER

```{r}
ind_i <- which(ls_preprocessed$pData_rnaseq$n_op2 == 'ind')
agg_i <- which(ls_preprocessed$pData_rnaseq$n_op2 == 'agg')

mat_ind <- as.matrix(data[,ind_i])
mat_agg <- as.matrix(data[,agg_i])

# Generating NULL model
dnull <- ttestNull(mat_agg, mat_ind, per=1000)

# Generating signature
signature <- rowTtest(mat_agg, mat_ind)
signature <- (qnorm(signature$p.value/2, lower.tail = FALSE) * sign(signature$statistic))[, 1]

# Running msVIPER
mrs <- msviper(signature, regu, dnull, verbose = FALSE)
```

VIPER plot showing the projection of the negative (repressed, shown in blue color) and positive (activated, shown in red color) targets for each TF, as inferred by ARACNe and correlation analysis when reverse engineering the regulatory network (vertical lines resembling a bar-code), on the GES (x-axis), where the genes in the GES were rank-sorted from the one most down-regulated to the one most upregulated in the 'test' vs 'reference' conditions.
The optional two-columns heatmap displayed on the right side of the figure shows the inferred differential activity (first column) and differential expression (second column), with the rank of the displayed genes in the GES (shown all the way to the right).

```{r}
knitr::kable(summary(mrs))
plot(mrs, cex = .7)
```

### Leading-edge analysis

To identify the genes driving the enrichment of a gene-set on a gene expression signature (GES) based on Gene Set Enrichment Analysis (GSEA).

```{r}
mrs <- ledge(mrs)
knitr::kable(summary(mrs))
```

```{r eval = FALSE, echo = FALSE}
# Shadow analysis
mrshadow <- shadow(mrs, regulators = 25, verbose = FALSE)
summary(mrshadow)
knitr::kable(summary(mrshadow))

# Synergy analysis
mrs <- msviperCombinatorial(mrs, regulators = 25, verbose = FALSE)
mrs <- msviperSynergy(mrs, verbose = FALSE)
knitr::kable(summary(mrs))
plot(mrs)
```

# Deconvolution Results

```{r}
mcp_dcv <- data.frame(t(read.delim("~/Documents/Massion_lab/RNASeq_summary/deconvolution/output/rna_only/MCP/mcp_fpkm_dcv.txt", row.names=1)))
qts_dcv <- data.frame(t(read.delim("~/Documents/Massion_lab/RNASeq_summary/deconvolution/output/rna_only/QTS/qts_fpkm_dcv.txt", row.names=1)))
cbs_dcv <- read.delim("~/Documents/Massion_lab/RNASeq_summary/deconvolution/output/rna_only/CBS/CIBERSORT.rna_only_fpkm.txt", row.names=1)
xcell_dcv <- data.frame(t(read.delim("~/Documents/Massion_lab/RNASeq_summary/deconvolution/output/rna_only/XCELL/xCell_rnaseq_fpkm_xCell_1132060320.txt", row.names=1)))

# From Pancaldi lab signatures
main_path = '/Users/senosam/Documents/Massion_lab/RNASeq_summary/deconvolution/output/rna_only/Pancaldi'
Epidish_BPRNACan_dcv <- read.delim(file.path(main_path,"Epidish_BPRNACan_dcv.txt"), 
                                   row.names=1)
DeconRNASeq_BPRNACan_dcv <- read.delim(file.path(main_path,"DeconRNASeq_BPRNACan_dcv.txt"), 
                                       row.names=1)
Epidish_BPRNACan3DProMet_dcv <- read.delim(file.path(main_path,"Epidish_BPRNACan3DProMet_dcv.txt"), 
                                           row.names=1)
DeconRNASeq_BPRNACan3DProMet_dcv <- read.delim(file.path(main_path,"DeconRNASeq_BPRNACan3DProMet_dcv.txt"), 
                                               row.names=1)
Epidish_BPRNACanProMet_dcv <- read.delim(file.path(main_path,"Epidish_BPRNACanProMet_dcv.txt"), 
                                         row.names=1)
DeconRNASeq_BPRNACanProMet_dcv <- read.delim(file.path(main_path,"DeconRNASeq_BPRNACanProMet_dcv.txt"), 
                                             row.names=1)
```

## XCell

```{r  , fig.width = 10, fig.height = 8}
frac_hm(xcell_dcv, pData_rnaseq, 'n_op2')
```

```{r  , fig.width = 20, fig.height = 15}
frac_boxplot(xcell_dcv, pData_rnaseq, 'n_op2')
```

## CIBERSORT

```{r  , fig.width = 10, fig.height = 8}
frac_hm(cbs_dcv[,1:22], pData_rnaseq, 'n_op2')
```

```{r  , fig.width = 20, fig.height = 15}
frac_boxplot(cbs_dcv[,1:22], pData_rnaseq, 'n_op2')
```

## quanTIseq

```{r  , fig.width = 10, fig.height = 8}
frac_hm(qts_dcv, pData_rnaseq, 'n_op2')
```

```{r  , fig.width = 20, fig.height = 15}
frac_boxplot(data.frame(qts_dcv), pData_rnaseq, 'n_op2')
```

## MCP counter

```{r  , fig.width = 10, fig.height = 8}
frac_hm(mcp_dcv, pData_rnaseq, 'n_op2')
```

```{r  , fig.width = 20, fig.height = 15}
frac_boxplot(data.frame(mcp_dcv), pData_rnaseq, 'n_op2')
```

## Epidish_BPRNACan

```{r  , fig.width = 10, fig.height = 8}
frac_hm(Epidish_BPRNACan_dcv, pData_rnaseq, 'n_op2')
```

```{r  , fig.width = 20, fig.height = 15}
frac_boxplot(data.frame(Epidish_BPRNACan_dcv), pData_rnaseq, 'n_op2')
```

## DeconRNASeq_BPRNACan

```{r  , fig.width = 10, fig.height = 8}
frac_hm(DeconRNASeq_BPRNACan_dcv, pData_rnaseq, 'n_op2')
```

```{r  , fig.width = 20, fig.height = 15}
frac_boxplot(data.frame(DeconRNASeq_BPRNACan_dcv), pData_rnaseq, 'n_op2')
```

## Epidish_BPRNACan3DProMet

```{r  , fig.width = 10, fig.height = 8}
frac_hm(Epidish_BPRNACan3DProMet_dcv, pData_rnaseq, 'n_op2')
```

```{r  , fig.width = 20, fig.height = 15}
frac_boxplot(data.frame(Epidish_BPRNACan3DProMet_dcv), pData_rnaseq, 'n_op2')
```

## DeconRNASeq_BPRNACan3DProMet

```{r  , fig.width = 10, fig.height = 8}
frac_hm(DeconRNASeq_BPRNACan3DProMet_dcv, pData_rnaseq, 'n_op2')
```

```{r  , fig.width = 20, fig.height = 15}
frac_boxplot(data.frame(DeconRNASeq_BPRNACan3DProMet_dcv), pData_rnaseq, 'n_op2')
```

## Epidish_BPRNACanProMet

```{r  , fig.width = 10, fig.height = 8}
frac_hm(Epidish_BPRNACanProMet_dcv, pData_rnaseq, 'n_op2')
```

```{r  , fig.width = 20, fig.height = 15}
frac_boxplot(data.frame(Epidish_BPRNACanProMet_dcv), pData_rnaseq, 'n_op2')
```

## DeconRNASeq_BPRNACanProMet

```{r  , fig.width = 10, fig.height = 8}
frac_hm(DeconRNASeq_BPRNACanProMet_dcv, pData_rnaseq, 'n_op2')
```

```{r  , fig.width = 20, fig.height = 15}
frac_boxplot(data.frame(DeconRNASeq_BPRNACanProMet_dcv), pData_rnaseq, 'n_op2')
```
